Designing an effective intervention of motivational interview using sequence classification methods

### 2017-03-01 paper/AMIA/main.tex
update data collection subsection

\section*{Methods}
\subsection*{\textit{Data collection}}
The experimental data sets for this work were constructed based on the transcripts of 37 motivational interview sessions, which include a total of 11,353 segmented and annotated utterances. Since clinical researchers tried to increase the desire and ability of adolescent to change their current behavior to target behavior, we used sequences from adolescent session and excluded sequences from caregiver session in the MI transcript. The utterances were annotated based on MYSCOPE codebook \cite{carcone2013provider} with 115 different behavior codes, which are grouped into the youth, caregiver, and counselor code groups. These utterances are then scanned from first to last and divided into successful and unsuccessful sequences when a commitment or change talk is found. A total of 1072 sequences have been observed which further partitioned into two subsets based on the outcome of motivational interviews: one data set that includes all sequences of positive change talk or commitment language (880 sequences) and the other data set which includes utterances ended with negative change talk or commitment language (192 sequences). Alternate sequences are the possible combination of normal sequence. For example, there are 6 possible alternate sequences for the following sequences: (C1, A1, A2, C2, C3, C4, A3), where adolescent and counselor codes are represented by A and C, respectively. Therefore, (C1, A1, C2, A3), (C1, A1, C3, A3), (C1, A1, C4, A3), (C1, A2, C2, A3), (C1, A2, C3, A3) and (C1, A2, C4, A3) were used as alternate sequences for the above sequence. A total of 18753 alternate sequences have been observed which further partitioned into two subsets of 18139 successful sequences and 614 unsuccessful sequences. In our experiment, normal and alternate sequences are employed with two subsets (successful and unsuccessful) to train Markov chain and HMM. Dataset statistics and a fragment of an adolescent session transcript are presented in Table~\ref{tab:data_dist} and Table~\ref{tab:anno_examp}. \\

>>>>

\section*{Methods}
\subsection*{\textit{Data collection}}
The experimental data sets for this work were constructed based on the transcripts of 37 motivational interview sessions, which include a total of 11,353 segmented and annotated utterances. Since clinical researchers tried to increase the desire and ability of adolescent to change their current behavior to target behavior, we used sequences from adolescent session and excluded sequences from caregiver session in the MI transcript. The utterances were annotated based on MYSCOPE codebook \cite{carcone2013provider} with 115 different behavior codes, which are grouped into the youth, caregiver, and counselor code groups. These utterances are then scanned from first to last and divided into successful and unsuccessful sequences when a commitment or change talk is found. A total of 1072 sequences have been observed which further partitioned into two subsets based on the outcome of motivational interviews: one data set that includes all sequences of positive change talk or commitment language (880 sequences) and the other data set which includes utterances ended with negative change talk or commitment language (192 sequences). Alternate sequences are the possible combination of normal sequence where two consecutive codes can not be come from same speaker. For example, there are 6 possible alternate sequences for the following sequences: (C1, A1, A2, C2, C3, C4, A3), where adolescent and counselor codes are represented by A and C, respectively. Therefore, (C1, A1, C2, A3), (C1, A1, C3, A3), (C1, A1, C4, A3), (C1, A2, C2, A3), (C1, A2, C3, A3) and (C1, A2, C4, A3) were used as alternate sequences for the above sequence. A total of 18753 alternate sequences have been observed which further partitioned into two subsets of 18139 successful and 614 unsuccessful sequences. In our experiment, normal and alternate sequences are employed with two subsets (successful and unsuccessful) to train Markov chain and HMM. Dataset statistics and a fragment of an adolescent session transcript are presented in Table~\ref{tab:data_dist} and Table~\ref{tab:anno_examp}. \\
